Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-22 Paper/ms.tex
Updated Zs and Hs

The marginal likelihood for our model was
$\log(\mathcal{Z}) \approx -217.65$. Nested Sampling also allows for calculation
of the ``information'', or Kullback-Leibler divergence (a quantity in information
theory) from the prior to the posterior, which quantifies how much we learned about the parameters:
\begin{eqnarray}
\mathcal{H} &=& \int p(\theta | D) \log\left[\frac{p(\theta | D)}{p(\theta)}\right] \, d\theta
\end{eqnarray}
An intuitive interpretation of this quantity is the number of times the
prior distribution had to be compressed by a factor of $e$ (if the logarithm
in the formula is a natural logarithm) to get to the posterior distribution.
For the $\nu$ Oph data the information was $\mathcal{H} \approx 77.7$ nats
(natural units) or 111 bits, so the posterior is roughly $e^{-77}$ times the
volume of the prior.

@@

The marginal likelihood was $\log(\mathcal{Z}) \approx -618.04$ and the
information was $\mathcal{H} \approx 140.2$ nats. This compares favourably
to the marginal likelihood of $-640.1$ (for a 6-planet model)
found by \citet{fengji}, although it is unclear whether we used exactly the
same dataset.
Interestingly, the log-likelihood curve (Figure~\ref{fig:logl})
shows this problem has two phase transitions. While these do not affect the
posterior distribution (as they did for $\nu$ Oph), they would cause difficulties
if we tried to calculte the marginal likelihood using annealing.

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
It is a pleasure to thank Fengji Hou and David Hogg (NYU) for inspiring me to
finally work on this problem, and Phil Gregory (UBC) for writing so many
interesting papers on it. We also thank Tom Loredo (Cornell) and Dan
Foreman-Mackey (NYU) for interesting conversations and feedback.

>>>>

The marginal likelihood for our model was
$\log(\mathcal{Z}) \approx -220.5$. Nested Sampling also allows for calculation
of the ``information'', or Kullback-Leibler divergence (a quantity in information
theory) from the prior to the posterior, which quantifies how much we learned about the parameters:
\begin{eqnarray}
\mathcal{H} &=& \int p(\theta | D) \log\left[\frac{p(\theta | D)}{p(\theta)}\right] \, d\theta
\end{eqnarray}
An intuitive interpretation of this quantity is the number of times the
prior distribution had to be compressed by a factor of $e$ (if the logarithm
in the formula is a natural logarithm) to get to the posterior distribution.
For the $\nu$ Oph data the information was $\mathcal{H} \approx 76.6$ nats
(natural units) or 111 bits, so the posterior is roughly $e^{-76.6}$ times the
volume of the prior.

@@

The marginal likelihood was $\log(\mathcal{Z}) \approx -616.3$ and the
information was $\mathcal{H} \approx 130.4$ nats. This compares favourably
to the marginal likelihood of $-640.1$ (for a 6-planet model)
found by \citet{fengji}, although it is unclear whether we used exactly the
same dataset.
Interestingly, the log-likelihood curve (Figure~\ref{fig:logl})
shows this problem has two phase transitions. While these do not affect the
posterior distribution (as they did for $\nu$ Oph), they would cause difficulties
if we tried to calculte the marginal likelihood using annealing.

@@

\vspace{-0.5cm}
\section*{Acknowledgements}
It is a pleasure to thank Fengji Hou and David Hogg (NYU) for inspiring me to
finally work on this problem, and Phil Gregory (UBC) for writing so many
interesting papers on it. We also thank Tom Loredo (Cornell) and Dan
Foreman-Mackey (NYU) for interesting conversations and feedback, and Ben
Montet (Caltech) and Geraint Lewis (Sydney) for helpful discussions.
